An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-21 EconGrowth.Rnw
Now also including ZA in the CES fits.

    # So, for the final fit, I'll put rho1 = 0.0 and rho = 0.0. The final R^2 = 

@@

@@

# print("")
print("CN Q")
print(summary(cesModel("CN", "Q")))
# 
# print("")
# print("ZA Q")
# print(summary(cesModel("ZA", "Q")))
# 
# print("")
# print("SA Q")
# print(summary(cesModel("SA", "Q")))
# 
# print("")
# print("IR Q")
# print(summary(cesModel("IR", "Q")))
# 
# print("")
# print("TZ Q")
# print(summary(cesModel("TZ", "Q")))
# 
# print("")
# print("ZM Q")
# print(summary(cesModel("ZM", "Q")))

>>>>

    # So, for the final fit, I'll put rho1 = 0.0 and rho = 0.0. The final R^2 = 0.9983.

@@

  } else if (countryAbbrev == "ZA"){
    # An unconstrained fit works for South Africa.  Results are sigma1 = 0.05, signalling complementarity
    # between k and l.  sigma = 0.03, indicating complementatity between (kl) and (e).
  } else if (countryAbbrev == "SA"){

@@

# print("")
# print("CN Q")
# print(summary(cesModel("CN", "Q")))
# 
# print("")
# print("ZA Q")
# print(summary(cesModel("ZA", "Q")))
# 
# print("")
print("SA Q")
print(summary(cesModel("SA", "Q")))
# 
# print("")
# print("IR Q")
# print(summary(cesModel("IR", "Q")))
# 
# print("")
# print("TZ Q")
# print(summary(cesModel("TZ", "Q")))
# 
# print("")
# print("ZM Q")
# print(summary(cesModel("ZM", "Q")))
